\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Algebra First-Year Exam, May 2020, Part 1},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\renewcommand{\labelenumi}{\textbf{\theenumi.}}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\newenvironment{examproblems}[1]{%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\section{\@startsection{section}{1}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=Title}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/algebra-first-year/}{Algebra First-Year Exam}, May 2020, Part 1\par}%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Algebra First-Year Exam, May 2020, Part 1}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examinstructions}
Do four out of the six problems below. If you hand in more than four problems, only the first four will be graded. You may (within reason) use results from the text if you state them fully.
\end{examinstructions}
\begin{examproblems}{0}
\item
Suppose that~\(M\) and~\(N\) are normal subgroups of a group~\(G\).
\begin{examsubparts}
\item[\textnormal{(i)}]
Show that \(G/(M \cap N)\) is isomorphic to a subgroup of \(G/M \times G/N\).
\item[\textnormal{(ii)}]
Show that if \(G=MN\), then in fact \(G/(M \cap N) \simeq G/M \times G/N\).
\end{examsubparts}
\item
This problem has two parts.
\begin{examsubparts}
\item[\textnormal{(i)}]
Find a representative for each conjugacy class of elements of order 4 in \(A_8\).
\item[\textnormal{(ii)}]
Describe the centralizer of each such representative as a suitable semidirect product.
\end{examsubparts}
\item
Suppose~\(G\) is a group of order \(351=3^3 \cdot 13\). Show that~\(G\) has a normal Sylow subgroup.
\item
List all isomorphism classes of abelian groups of order 16. One of these has an automorphism of order 5; which is it?
\item
Suppose~\(G\) is a solvable group, \(H \subseteq G\) is a nontrivial normal subgroup. Show that~\(H\) has a nontrivial abelian subgroup that is normal in~\(G\) (consider the derived series of~\(H\)).
\item
Construct four nonisomorphic groups of order 28 (use a semidirect product for one case).
\end{examproblems}
\end{document}
