\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Complex Analysis PhD Exam, May 2009},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Complex Analysis PhD Exam, May 2009}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/complex-analysis-phd/}{Complex Analysis PhD Exam}, May 2009\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Complex Analysis PhD Exam, May 2009}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examinstructions}
Give complete proofs and computations. Partial credit will be given where justified. In the following, \(\mathbb{C}\) denotes the set of complex numbers and \(D=\{z\in\mathbb{C}\mid |z|<1\}\).
\end{examinstructions}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
Assume that~\(f\) is an entire function with \(f(0)=0\). Consider the family of functions \(\{f_n\}\), where \(f_n\) is the \(n^{\text{th}}\) iterate of~\(f\), i.e. \(f_n=f\circ f\circ\cdots\circ f\) (\(n\) times).
\begin{examsubparts}
\item[\textnormal{(a)}]
If \(|f'(0)|<1\), show there is a open set~\(U\) containing zero so that the family \(\{f_n\}\) is normal when restricted to~\(U\).
\item[\textnormal{(b)}]
If \(|f'(0)|>1\), show there is no open set~\(U\) containing zero so that the family \(\{f_n\}\) is normal when restricted to~\(U\).
\end{examsubparts}
\def\ProblemHeadingText{Problem 2.}
\item
Let~\(G\) and \(G'\) be open, simply connected proper subsets of~\(\mathbb{C}\). Show that for any pair of points \(p\in G\) and \(p'\in G'\) there is a bijective, analytic function \(f:G\to G'\) with \(f(p)=p'\).
\def\ProblemHeadingText{Problem 3.}
\item
This problem has two parts.
\begin{examsubparts}
\item[\textnormal{(a)}]
Show that
\[
\prod_{n=2}^{\infty}\left(1-\frac{1}{n^2}\right)=\frac{1}{2}.
\]
\item[\textnormal{(b)}]
For which values of~\(z\) does the following product converge?
\[
\prod_{n=0}^{\infty}(1+z^{3n})
\]
\end{examsubparts}
\def\ProblemHeadingText{Problem 4.}
\item
Find an explicit biholomorphism from the semidisk \(E:=\{z\mid |z|<1,\operatorname{Re}(z)>0\}\) onto the unit disk~\(D\).
\def\ProblemHeadingText{Problem 5.}
\item
Let \(0<a<1\). Evaluate the integral
\[
\int_0^\infty \frac{x^{a-1}}{1+x}\,dx.
\]
\def\ProblemHeadingText{Problem 6.}
\item
Let~\(f\) be an entire function of finite order. Prove that if the order is not an integer, then~\(f\) must have infinitely many zeros. Does there exist an entire function of infinite order with finitely many zeros? Explain.
\def\ProblemHeadingText{Problem 7.}
\item
Let~\(f\) be entire and assume that there exist \(M,R>0\) and \(n\in\mathbb{N}\) such that \(|f(z)|\leq M|z|^n\) for all \(z\in\mathbb{C}\setminus B(0;R)\). Prove that~\(f\) is a polynomial of degree less than or equal to~\(n\).
\def\ProblemHeadingText{Problem 8.}
\item
Let~\(f\) have a power series expansion about~\(0\) with radius of convergence~\(1\). Assume, in addition, that all of the coefficients of this power series expansion are greater than or equal to zero. Prove that~\(1\) must be a singular point for~\(f\).
\end{examproblems}
\end{document}
