\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Analysis PhD Exam, January 2012},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Analysis PhD Exam, January 2012}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/analysis-phd/}{Analysis PhD Exam}, January 2012\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Analysis PhD Exam, January 2012}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examinstructions}
Answer SIX questions. Write solutions in a neat and logical fashion, giving complete reasons for all steps and stating carefully any substantial theorems used.
\end{examinstructions}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
Let~\(V\) be the vector space of all complex sequences \(z=(z_n)_{n\in\mathbb N}\) and for each \(n\in\mathbb N\) denote the~\(n\)th coordinate map by
\[
\phi_n:V\to\mathbb C:z\mapsto z_n.
\]
 Does~\(V\) carry a norm relative to which the linear functional \(\phi_n\) is bounded for infinitely many values of~\(n\)? Explain.
\def\ProblemHeadingText{Problem 2.}
\item
State the Baire Category Theorem.

\par
Decide whether the vector space \(c_{00}\) comprising all finitely-nonzero complex sequences carries a complete norm (by considering suitable subspaces of finite dimension, or otherwise).
\def\ProblemHeadingText{Problem 3.}
\item
State the Closed Graph Theorem.

\par
Prove the Banach Isomorphism Theorem.
\def\ProblemHeadingText{Problem 4.}
\item
Let \(1\leq p<\infty\) and define norms \(\|\cdot\|_p\) and \(\|\cdot\|_\infty\) on \(C[0,1]\ni f\) by
\[
\|f\|_p=\left(\int_0^1|f(t)|^p\,dt\right)^{1/p}
\]

\[
\|f\|_\infty=\sup\{|f(t)|:0\leq t\leq1\}
\]
 as usual. Show that on \(C[0,1]\):
\begin{examsubparts}
\item[\textnormal{(i)}]
\(\|\cdot\|_p\) and \(\|\cdot\|_\infty\) are inequivalent;
\item[\textnormal{(ii)}]
\(\|\cdot\|_p\) is incomplete.
\end{examsubparts}
\def\ProblemHeadingText{Problem 5.}
\item
Let \(\mathbb H\) be a complex Hilbert space and \(\phi:\mathbb H\to\mathbb C\) a bounded linear functional. Prove that there exists a unique \(u\in\mathbb H\) such that \(\phi(v)=\langle u\mid v\rangle\) for each \(v\in\mathbb H\).
\def\ProblemHeadingText{Problem 6.}
\item
Say what it means for one measure to be absolutely continuous relative to another.

\par
Let \((\mu_n)_{n=1}^{\infty}\) be a sequence of finite measures on the~\(\sigma\)-algebra \(\mathcal F\). Prove that there exists a finite measure~\(\lambda\) on \(\mathcal F\) such that \(\mu_n\ll\lambda\) for each \(n\geq1\).
\def\ProblemHeadingText{Problem 7.}
\item
Let \((\Omega,\mathcal F,\mu)\) be a finite measure space on which~\(f\) is a measurable real-valued function. Prove that the rule
\[
t\in\mathbb R\Rightarrow F(t)=\int_\Omega e^{itf(\omega)}\,d\mu(\omega)
\]
 defines a continuous function \(F:\mathbb R\to\mathbb C\).
\def\ProblemHeadingText{Problem 8.}
\item
Let \((\Omega,\mathcal F,\mu)\) be a~\(\sigma\)-finite measure space, let \(g:\Omega\to\mathbb C\) be measurable and let \(p\geq1\). Show that pointwise multiplication
\[
f\in L_p\Rightarrow\Phi_g(f)=gf
\]
 defines a bounded linear operator \(\Phi_g\) on \(L_p\) iff \(g\in L_\infty\). Note: Recall that \(g\in L_\infty\) iff there exists \(K\geq0\) such that \(\mu\{|g|>K\}=0\).
\end{examproblems}
\end{document}
