\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Combinatorics PhD Exam, August 2025},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Combinatorics PhD Exam, August 2025}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/combinatorics-phd/}{Combinatorics PhD Exam}, August 2025\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Combinatorics PhD Exam, August 2025}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
Find the number of sequences of length \(n \leq 26\) of letters from the alphabet, each such sequence required to be in alphabetical order with no letter repeated.
\def\ProblemHeadingText{Problem 2.}
\item
Let \(n \geq 3\) be an odd number. Prove that the sequence
\[
\binom{n}{1},\binom{n}{2},\ldots,\binom{n}{\frac{n-1}{2}}
\]
 contains an odd number of odd numbers.
\def\ProblemHeadingText{Problem 3.}
\item
Find a second order linear recurrence for the number of ways to properly 3-color an~\(n\)-cycle. (No two adjacent vertices receive the same color.)
\def\ProblemHeadingText{Problem 4.}
\item
In a tournament, each player plays every other player exactly once, except in the process 3 players dropped out after playing exactly 2 games each. If 50 games were played, how many games were played just among the 3 players who dropped out? Explain your answer.
\def\ProblemHeadingText{Problem 5.}
\item
Suppose a convex polyhedron has 6 vertices and 12 edges. Prove that each facet is a triangle.
\def\ProblemHeadingText{Problem 6.}
\item
Let \(A(n)\) be the number of set partitions of \([n]\) such that~\(i\) and \(i+1\) never occur in the same block for any \(i=1,2,\ldots,n-1\). Show that
\[
A(n)=\sum_{i=0}^{n-1}(-1)^i\binom{n-1}{i}B(n-i),
\]
 where \(B(n)\) is the \(n^{th}\) Bell number. Alternatively, show that
\[
A(n)=B(n-1).
\]
\def\ProblemHeadingText{Problem 7.}
\item
Let~\(P\) be a finite poset with a bottom element~\(0\). Show that if~\(x\) covers exactly one element of~\(P\), then
\[
\mu(x,0)=
\begin{cases}
-1 & \text{if }x\text{ covers }0,\\
0 & \text{otherwise.}
\end{cases}
\]
 For any \(n\in\mathbb{Z}\), construct a poset containing an element~\(x\) with \(\mu(x)=n\).
\def\ProblemHeadingText{Problem 8.}
\item
Prove that a simple~\(k\)-regular graph with girth~\(k\) has order at least \(2k\).
\end{examproblems}
\end{document}
