\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Topology First-Year Exam, May 2022, Part 1},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Topology First-Year Exam, May 2022, Part 1}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/topology-first-year/}{Topology First-Year Exam}, May 2022, Part 1\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Topology First-Year Exam, May 2022, Part 1}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examinstructions}
Do seven 7 and only seven of the following.
\end{examinstructions}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
Let~\(X\) be a set, and let \(\mathcal T\) be the collection of all subsets~\(A\) of~\(X\) such that \(X-A\) is either finite or all of~\(X\).
\begin{examsubparts}
\item[\textnormal{(a)}]
Prove that \((X,\mathcal T)\) is topological space.
\item[\textnormal{(b)}]
Now let \(X=\mathbb R\), the real line.
\begin{examsubparts}
\item[\textnormal{(i)}]
Determine if the sequence \(x_n=7n+8\) converges and if so, to which point or points.
\item[\textnormal{(ii)}]
Show that every infinite set is connected.
\item[\textnormal{(iii)}]
What is \(\overline{\{5\}}\)?
\end{examsubparts}
\end{examsubparts}
\def\ProblemHeadingText{Problem 2.}
\item
Let~\(X\) be a topological space. Let \(D=\{(x,y)\in X\times X:x=y\}\). Prove that~\(X\) is a Hausdorff space if and only if~\(D\) is a closed subset of \(X\times X\), where \(X\times X\) has the product topology.
\def\ProblemHeadingText{Problem 3.}
\item
Show that \(\mathbb R^{\mathbb Z_+}\) with the uniform topology is not connected.
\def\ProblemHeadingText{Problem 4.}
\item
A chain of subsets is a collection \(A_n\) for \(n\in\mathbb Z_+\) with the property that for all~\(i\), \(A_i\cap A_{i+1}\ne\varnothing\). If each \(A_n\) in a chain is connected, show that \(\bigcup_{n\in\mathbb Z_+}A_n\) is also connected.
\def\ProblemHeadingText{Problem 5.}
\item
If~\(A\) is a countable set, show that \(\mathbb R^2-A\) is path connected.
\def\ProblemHeadingText{Problem 6.}
\item
A space is called locally Baire if every point has an open neighborhood that is a Baire space. Prove that locally Baire implies Baire.
\def\ProblemHeadingText{Problem 7.}
\item
Show that the Tietze Extension Theorem implies Urysohn’s Lemma.
\def\ProblemHeadingText{Problem 8.}
\item
Assume that \((X,d)\) is metric. Show the following
\begin{examsubparts}
\item[\textnormal{(a)}]
\(X\) is normal
\item[\textnormal{(b)}]
If~\(X\) is compact then it is second countable
\end{examsubparts}
\end{examproblems}
\end{document}
