\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Probability PhD Exam, September 1989},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Probability PhD Exam, September 1989}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/probability-phd/}{Probability PhD Exam}, September 1989\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Probability PhD Exam, September 1989}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
Let \(\{\overline{X}_m\}\) be a submartingale and~\(T\) a stopping time such that \(E[T]<\infty\). Assume \(E[|\overline{X}_{m+1}-\overline{X}_m|\mid\mathcal F_m]\le M\) on \((T>m)\) for some constant~\(M\). Show that \(\overline{X}_T\) is integrable and \(E[\overline{X}_0]\le E[\overline{X}_T]\).
\def\ProblemHeadingText{Problem 2.}
\item
Let \(\overline{X}_m\to\overline{X}\) in probability. Let~\(f\) be continuous on \(\mathbb R^1\). Then \(f(\overline{X}_m)\to f(\overline{X})\) in probability. Prove this.
\def\ProblemHeadingText{Problem 3.}
\item
Can convergence a.e. be given by a metric? In other words, is there a metric~\(\rho\) such that \(\rho(\overline{X}_m,0)\to0\) is equivalent to \(\overline{X}_m\to0\) a.e.? Substantiate.
\def\ProblemHeadingText{Problem 4.}
\item
Explain the notion of convergence in distribution. Let \(\overline{X}_m\to\overline{X}\) in distribution. Does it follow that \(\overline{X}_m\to\overline{X}\) in probability? Suppose \(P[\overline{X}=a]=1\). Is it then true that \(\overline{X}_m\to\overline{X}\) in probability? Substantiate all your answers.
\def\ProblemHeadingText{Problem 5.}
\item
Let \(\overline{Y}\in L^p\), \(|\overline{X}_m|\le\overline{Y}\), and \(\overline{X}_m\to\overline{X}\) in distribution. Show that \(E(|\overline{X}_m|^p)\to E(|\overline{X}|^p)\).
\def\ProblemHeadingText{Problem 6.}
\item
Given that~\(f\) is a characteristic function and \(|f(1/2)|=1\), what can you conclude?
\def\ProblemHeadingText{Problem 7.}
\item
State and give a sketch of the proof of the strong law of large numbers.
\def\ProblemHeadingText{Problem 8.}
\item
Let \(\overline{X}_m\) be i.i.d., \(E[\overline{X}_m]=0\), \(E[\overline{X}_m^2]=1\). Can this sequence be complete orthonormal? Substantiate.
\def\ProblemHeadingText{Problem 9.}
\item
Let~\(\mu\) be a non-trivial infinitely divisible distribution on \(\mathbb R^1\). Prove that~\(\mu\) cannot have compact support.
\end{examproblems}
\end{document}
