\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Analysis First-Year Exam, January 2023, Part 1},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Analysis First-Year Exam, January 2023, Part 1}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/analysis-first-year/}{Analysis First-Year Exam}, January 2023, Part 1\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Analysis First-Year Exam, January 2023, Part 1}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examinstructions}
Answer FOUR questions in detail. State carefully any results used without proof.
\end{examinstructions}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
Let \((a_n)\) and \((b_n)\) be bounded real sequences. Prove that
\[
\limsup(a_n+b_n)\leq \limsup a_n+\limsup b_n
\]
 with equality when \((a_n)\) converges.
\def\ProblemHeadingText{Problem 2.}
\item
Let~\(A\) be a subset of the metric space \((M,d)\) and define \(d_A:M\to\mathbb{R}\) by \(d_A(x)=\inf\{d(a,x):a\in A\}\). Prove that:
\begin{examsubparts}
\item[\textnormal{(i)}]
\(d_A\) is uniformly continuous;
\item[\textnormal{(ii)}]
\(\{x\in M:d_A(x)=0\}=\overline{A}\).
\end{examsubparts}
\def\ProblemHeadingText{Problem 3.}
\item
Let~\(X\) and~\(Y\) be metric spaces; let \(f:X\to Y\) be a continuous bijection, with inverse \(g:Y\to X\). For each of the following statements, provide a proof if true or a counterexample (with justification) if false:
\begin{examsubparts}
\item[\textnormal{(i)}]
if~\(X\) is compact then~\(g\) is continuous;
\item[\textnormal{(ii)}]
if~\(Y\) is compact then~\(g\) is continuous.
\end{examsubparts}
\def\ProblemHeadingText{Problem 4.}
\item
Let~\(X\) and~\(Y\) be metric spaces; let \(f:X\to Y\) be a continuous bijection, with uniformly continuous inverse \(g:Y\to X\). For each of the following statements, provide a proof if true or a counterexample if false:

\par
[Be sure to demonstrate uniform continuity of~\(g\) in any counterexample.]
\begin{examsubparts}
\item[\textnormal{(i)}]
if~\(X\) is complete then~\(Y\) is complete;
\item[\textnormal{(ii)}]
if~\(Y\) is complete then~\(X\) is complete.
\end{examsubparts}
\def\ProblemHeadingText{Problem 5.}
\item
The function \(f:\mathbb{R}\to\mathbb{R}\) is differentiable, with \(|f'|\leq 1\) everywhere. Prove that if \(\varepsilon>0\) is sufficiently small (how small?) then the function \(F:\mathbb{R}\to\mathbb{R}\) defined by \(F(x)=x+\varepsilon f(x)\) is injective.
\end{examproblems}
\end{document}
