\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Analysis First-Year Exam, January 2018, Part 1},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Analysis First-Year Exam, January 2018, Part 1}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/analysis-first-year/}{Analysis First-Year Exam}, January 2018, Part 1\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Analysis First-Year Exam, January 2018, Part 1}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examinstructions}
Answer FOUR questions in detail. State carefully any results used without proof.
\end{examinstructions}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
Let \((a_n:n\ge 0)\) be a bounded real sequence. For each \(N\ge 0\) define \(\bar a_N=\sup\{a_n:n\ge N\}\) and let \(s=\inf\{\bar a_N:N\ge 0\}\). Prove:
\begin{examsubparts}
\item[\textnormal{(i)}]
if \(s<t\) then \(a_n<t\) eventually, in the sense \((\exists N)(\forall n\ge N)(a_n<t)\);
\item[\textnormal{(ii)}]
if \(s>r\) then \(a_n>r\) frequently, in the sense \((\forall N)(\exists n\ge N)(a_n>r)\).
\end{examsubparts}
\def\ProblemHeadingText{Problem 2.}
\item
Let~\(X\) be a metric space. Assume that there exists \(\delta>0\) such that the distance between distinct points of~\(X\) is always~\(\delta\) or greater. Determine precisely which subsets of~\(X\) are open, which closed, which compact and which connected.
\def\ProblemHeadingText{Problem 3.}
\item
Let \(f:X\to\mathbb{R}\) have the property that if~\(a\) is any real number then \(U(a)=\{x:f(x)<a\}\) is an open subset of the compact metric space~\(X\).
\begin{examsubparts}
\item[\textnormal{(i)}]
Prove that~\(f\) is bounded above on~\(X\).
\item[\textnormal{(ii)}]
Prove that \(s=\sup\{f(x):x\in X\}\) is a value of~\(f\). For (ii): suppose~\(s\) not a value and consider the function \(F=1/(s-f)\).
\end{examsubparts}
\def\ProblemHeadingText{Problem 4.}
\item
Let \(f:X\to Y\) be a bijection between metric spaces; assume that~\(Y\) is complete and that \(f^{-1}\) is continuous.
\begin{examsubparts}
\item[\textnormal{(i)}]
Show that if~\(f\) is uniformly continuous then~\(X\) is complete.
\item[\textnormal{(ii)}]
Show that if~\(f\) is only continuous then~\(X\) can fail to be complete.
\end{examsubparts}
\def\ProblemHeadingText{Problem 5.}
\item
Let \(f:(a,b)\to\mathbb{R}\) be differentiable and assume that its derivative \(f'\) is bounded. Prove that the right-hand limit \(\lim_{t\to a+}f(t)\) exists.
\end{examproblems}
\end{document}
