\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Topology First-Year Exam, January 2024, Part 2},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Topology First-Year Exam, January 2024, Part 2}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/topology-first-year/}{Topology First-Year Exam}, January 2024, Part 2\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Topology First-Year Exam, January 2024, Part 2}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examinstructions}
For the first five problems, show all your work and support all statements.
\end{examinstructions}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
Let \(p\colon E \to B\) be a covering map, and let \(p(e_0)=b_0\). Prove that the lifting correspondence \(\phi\colon \pi_1(B,b_0) \to p^{-1}(b_0)\) is surjective if~\(E\) is path connected, and bijective if~\(E\) is simply connected.
\def\ProblemHeadingText{Problem 2.}
\item
Show that a continuous map \(f\colon S^1 \to S^1\) is homotopic to \(z^n\colon S^1 \to S^1\) (given by \(e^{i\theta} \mapsto e^{in\theta}\)) for some integer \(n\in\mathbb Z\).
\def\ProblemHeadingText{Problem 3.}
\item
State and prove the Brouwer fixed point theorem for the unit disk, \(D^2\).
\def\ProblemHeadingText{Problem 4.}
\item
The connected sum of two surfaces~\(S\) and \(S'\) is obtained by cutting out a disk from each surface and gluing the resulting surfaces along their circle boundaries: \(S\mathbin{\#}S'=(S\setminus D^2)\cup_{S^1}(S'\setminus D^2)\). Let~\(T\) be the torus. Using the Seifert–van Kampen theorem on the natural decomposition into two pieces given by the connected sum, calculate \(\pi_1(T\mathbin{\#}T)\).
\def\ProblemHeadingText{Problem 5.}
\item
Prove that if~\(X\) is path connected and \(x_0\) and \(x_1\) are two points of~\(X\), then \(\pi_1(X,x_0)\) is isomorphic to \(\pi_1(X,x_1)\).
\end{examproblems}
\begin{examinstructions}
Answer the following problems with complete definitions, complete statements, an example, or a short proof.
\end{examinstructions}
\begin{examproblems}{5}{H2}
\def\ProblemHeadingText{Problem 6.}
\item
State the Seifert–van Kampen theorem.
\def\ProblemHeadingText{Problem 7.}
\item
Show that the Tietze Extension Theorem implies Urysohn’s Lemma.
\def\ProblemHeadingText{Problem 8.}
\item
Let~\(X\) be a topological space. Define what it means for~\(X\) to be compact.
\def\ProblemHeadingText{Problem 9.}
\item
Let~\(X\) be a completely regular space. Define the Stone–Čech compactification of~\(X\).
\def\ProblemHeadingText{Problem 10.}
\item
State the Tychonoff Theorem.
\def\ProblemHeadingText{Problem 11.}
\item
Let \([0,1]^J\) be the set of all functions from a set~\(J\) to \([0,1]\). Prove that if \(\mathcal F\) is a closed subset of \([0,1]^J\), then \(\mathcal F\) is compact.
\def\ProblemHeadingText{Problem 12.}
\item
Let \(A\subset X\). Let \(r\colon X\to A\) be a retraction, meaning~\(r\) is continuous and \(r(a)=a\) for all \(a\in A\). Show that for any \(a_0\in A\), the induced map \(r_*\colon \pi_1(X,a_0)\to\pi_1(A,a_0)\) on the fundamental groups is surjective.
\def\ProblemHeadingText{Problem 13.}
\item
Let \(\gamma\colon [0,1]\to X\) be a loop with basepoint \(x_0\). Let \(\gamma^{-1}\) be defined by \(\gamma^{-1}(t)=\gamma(1-t)\). Show that \(\gamma*\gamma^{-1}\) is loop homotopic to the constant loop.
\def\ProblemHeadingText{Problem 14.}
\item
Describe a surface whose fundamental group is not abelian.
\def\ProblemHeadingText{Problem 15.}
\item
Let~\(X\) and~\(Y\) be topological spaces and let \(f\colon X\to Y\) be continuous and surjective. Show that if~\(X\) is connected, then so is~\(Y\).
\end{examproblems}
\end{document}
