\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Topology First-Year Exam, August 2024, Part 1},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Topology First-Year Exam, August 2024, Part 1}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/topology-first-year/}{Topology First-Year Exam}, August 2024, Part 1\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Topology First-Year Exam, August 2024, Part 1}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examinstructions}
For the first five problems, show all your work and support all statements.
\end{examinstructions}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
Let~\(X\) be a set. Show there is no bijection between~\(X\) and \(\mathcal{P}(X)\), the power set of~\(X\).
\def\ProblemHeadingText{Problem 2.}
\item
Show that \(\mathbb{R}^{\omega}\) with the box topology is not connected.
\def\ProblemHeadingText{Problem 3.}
\item
Show that if~\(X\) is a compact Hausdorff space, then~\(X\) is a regular space.
\def\ProblemHeadingText{Problem 4.}
\item
Let~\(A\) be a partially ordered set. The maximum principle states that there is a maximal totally ordered subset~\(B\) of~\(A\). Zorn’s lemma states that if every totally ordered subset of~\(A\) has an upper bound in~\(A\), then~\(A\) has a maximal element. Prove that the maximum principle implies Zorn’s lemma.
\def\ProblemHeadingText{Problem 5.}
\item
Let \((X,d)\) be a metric space. Suppose there exists some \(\varepsilon>0\) such that for all \(x\in X\), the closure \(\overline{B_\varepsilon(x)}\) of the~\(\varepsilon\)-ball about~\(x\) is compact. Prove that~\(X\) is complete.
\end{examproblems}
\begin{examinstructions}
Answer the following problems with complete definitions, complete statements, an example, or a short proof.
\end{examinstructions}
\begin{examproblems}{5}{H2}
\def\ProblemHeadingText{Problem 6.}
\item
Define what it means for a topological space~\(X\) to be normal.
\def\ProblemHeadingText{Problem 7.}
\item
Let~\(X\) be compact, and let \(C_1,C_2,C_3,\ldots\) be a sequence of closed sets in~\(X\). If \(\bigcap_{i=1}^{k}C_i\) is nonempty for all \(k\geq 1\), then prove that \(\bigcap_{i=1}^{\infty}C_i\) is nonempty.
\def\ProblemHeadingText{Problem 8.}
\item
Let \(\{A_n\}_{n\in\mathbb{Z}_+}\) be a countable collection of countable sets. Prove that the union \(\bigcup_{n\in\mathbb{Z}_+}A_n\) is countable.
\def\ProblemHeadingText{Problem 9.}
\item
Show that \([0,1]\) and \([0,1)\) are not homeomorphic.
\def\ProblemHeadingText{Problem 10.}
\item
Show that \(f:\mathbb{R}\to\mathbb{R}^{\omega}\) defined by \(f(x)=(x,x,x,\ldots)\) is not continuous if \(\mathbb{R}^{\omega}\) has the box topology.
\def\ProblemHeadingText{Problem 11.}
\item
Give an example of a topological space that is connected but not locally connected.
\def\ProblemHeadingText{Problem 12.}
\item
State the Baire Category Theorem.
\def\ProblemHeadingText{Problem 13.}
\item
Let \((x_n)\) be a Cauchy sequence in the metric space~\(X\). Show that if \((x_n)\) has a subsequence \((x_{n_k})\) that converges, then \((x_n)\) also converges.
\def\ProblemHeadingText{Problem 14.}
\item
Give an example of a metric space \((X,d)\) and a continuous function \(f:X\to X\) satisfying the following:
\begin{examsubparts}
\item[\textnormal{(i)}]
\(d(f(x),f(y))<d(x,y)\) for all distinct \(x,y\in X\),
\item[\textnormal{(ii)}]
\(f(x)\neq x\) for all \(x\in X\).
\end{examsubparts}
\def\ProblemHeadingText{Problem 15.}
\item
Let~\(X\) be a topological space. Suppose there is a space~\(Y\) such that the following conditions hold. Prove that~\(X\) is locally compact.
\begin{examsubparts}
\item[\textnormal{(i)}]
\(X\) is a subspace of~\(Y\),
\item[\textnormal{(ii)}]
\(Y\setminus X\) is a single point, and
\item[\textnormal{(iii)}]
\(Y\) is compact Hausdorff.
\end{examsubparts}
\end{examproblems}
\end{document}
