\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Algebra PhD Exam, August 2005},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Algebra PhD Exam, August 2005}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/algebra-phd/}{Algebra PhD Exam}, August 2005\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Algebra PhD Exam, August 2005}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examinstructions}
Answer seven problems. Write your answers clearly in complete English sentences. You may quote results (within reason) as long as you state them clearly.
\end{examinstructions}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
Let \(\mathcal C\) be a category and let~\(\Lambda\) be a set. For each \(\lambda\in\Lambda\), let \(X_\lambda\) be an object in \(\mathcal C\).
\begin{examsubparts}
\item[\textnormal{(a)}]
Give the definition of a product of the collection of objects \(\{X_\lambda\}_{\lambda\in\Lambda}\).
\item[\textnormal{(b)}]
Prove that any two products of the \(\{X_\lambda\}_{\lambda\in\Lambda}\) are isomorphic.
\item[\textnormal{(c)}]
Prove that products always exist in the category of groups.
\end{examsubparts}
\def\ProblemHeadingText{Problem 2.}
\item
Show that the alternating group \(A_n\) is a simple group for \(n\geq 5\). Show that the symmetric group \(S_n\) is not solvable for \(n\geq 5\).
\def\ProblemHeadingText{Problem 3.}
\item
State and prove Jacobson’s Density Theorem.
\def\ProblemHeadingText{Problem 4.}
\item
Consider the polynomial
\[
p(x)=x^5-3x^4-2x^2+2x+2
\]
 over \(\mathbb Q\). Can all the roots of \(p(x)\) be written by radicals over \(\mathbb Q\)? Can they be written by radicals over \(\mathbb C\)? Carefully justify both answers.
\def\ProblemHeadingText{Problem 5.}
\item
Suppose that~\(F\) is a finite extension of \(\mathbb Q\). Prove that~\(F\) contains only a finite number of roots of unity.
\def\ProblemHeadingText{Problem 6.}
\item
Let~\(F\) be the free group in generators~\(x\) and~\(y\). Let~\(N\) be the subgroup of~\(F\) generated by the set
\[
S=\{z^2:z\in F\}.
\]
 Prove that~\(N\) is a normal subgroup of~\(F\), and calculate the order of \(F/N\).
\def\ProblemHeadingText{Problem 7.}
\item
Let~\(A\) be a torsion abelian group, and let \(\mathbb Q\) be the (additive) group of the rational numbers. Prove that \(A\otimes_{\mathbb Z}\mathbb Q=\{0\}\), and that \(\mathbb Q\otimes_{\mathbb Z}\mathbb Q\cong\mathbb Q\).
\def\ProblemHeadingText{Problem 8.}
\item
Let~\(R\) be an integral domain with quotient field~\(F\). Suppose that \(a\in R\) is such that \(a\neq 0\) and \(1/a\) is integral over~\(R\). Prove that~\(a\) is a unit of~\(R\).
\def\ProblemHeadingText{Problem 9.}
\item
Let~\(R\) be a commutative ring with \(1\neq 0\). Prove that the set consisting of~\(0\) and all zero divisors in~\(R\) contains at least one prime ideal.
\def\ProblemHeadingText{Problem 10.}
\item
Let~\(R\) be a commutative ring with identity different from zero. Let \(F_1\) and \(F_2\) be two finitely generated free~\(R\)-modules, and assume that \(F_1\cong F_2\) as~\(R\)-modules. Prove that the cardinality of the set of free generators for \(F_1\) equals the cardinality of the set of free generators for \(F_2\).
\def\ProblemHeadingText{Problem 11.}
\item
Let~\(R\) and~\(S\) be semi-simple rings with exactly \(400\) elements. Assume that neither~\(R\) nor~\(S\) is commutative. Does it follow that \(R\cong S\)? Justify your answer.
\end{examproblems}
\end{document}
