\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Analysis First-Year Exam, May 2024, Part 2},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Analysis First-Year Exam, May 2024, Part 2}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/analysis-first-year/}{Analysis First-Year Exam}, May 2024, Part 2\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Analysis First-Year Exam, May 2024, Part 2}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examinstructions}
Answer FOUR questions in detail. State carefully any results used without proof.
\end{examinstructions}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
Let \(f:[a,b]\to\mathbb{R}\) be Riemann integrable, let~\(g\) be a real-valued function on \([a,b]\), and let \(D=\{t\in[a,b]:f(t)\ne g(t)\}\).
\begin{examsubparts}
\item[\textnormal{(i)}]
Show by example that if~\(D\) is countably infinite then~\(g\) can fail to be Riemann integrable.
\item[\textnormal{(ii)}]
Prove that if~\(D\) is finite then~\(g\) must be Riemann integrable.
\end{examsubparts}
\def\ProblemHeadingText{Problem 2.}
\item
Prove Dini’s theorem that, if the sequence \((f_n)_{n=0}^{\infty}\) of continuous real-valued functions on a compact space decreases pointwise to zero, then the convergence is uniform. Show by example that uniform convergence can fail if decreases pointwise is replaced by converges pointwise.
\def\ProblemHeadingText{Problem 3.}
\item
State the Weierstrass approximation theorem. Determine exactly which continuous functions \(f:[-1,1]\to\mathbb{R}\) satisfy the requirement that for each strictly positive integer~\(n\),
\[
\int_{-1}^{1}f(t)t^n\,dt=0.
\]
\def\ProblemHeadingText{Problem 4.}
\item
Let \((\Omega,\mathcal{A},\mu)\) be a measure space and let \((A_n)_{n=1}^{\infty}\) be a sequence in~\(\mathcal{A}\). For each positive integer~\(N\), let \(B_N\) be the set containing exactly those \(\omega\in\Omega\) that lie in \(A_n\) for at least~\(N\) values of~\(n\). By considering the series \(\sum_{n=1}^{\infty}\mathbf{1}_{A_n}\) of indicator functions, prove that
\[
N\mu(B_N)\leq\sum_{n=1}^{\infty}\mu(A_n).
\]
\def\ProblemHeadingText{Problem 5.}
\item
Let the non-negative function \(f:\mathbb{R}\to\mathbb{R}\) be integrable with respect to Lebesgue measure~\(\lambda\) and for each real~\(t\) define
\[
F(t)=\int_0^t f\,d\lambda.
\]
 Prove that the function~\(F\) is continuous. Must~\(F\) be uniformly continuous? Explain.
\end{examproblems}
\end{document}
