\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Topology First-Year Exam, January 2016, Part 1},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Topology First-Year Exam, January 2016, Part 1}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/topology-first-year/}{Topology First-Year Exam}, January 2016, Part 1\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Topology First-Year Exam, January 2016, Part 1}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\subsection{Part 1.}
\begin{examinstructions}
Complete Proofs. Support all statements to the best of your ability.
\end{examinstructions}
\begin{examproblems}{0}{H3}
\def\ProblemHeadingText{Problem 1.}
\item
Let~\(X\) be a topological space. Prove that if~\(X\) is path connected, then~\(X\) is connected.
\def\ProblemHeadingText{Problem 2.}
\item
Let~\(X\) be a topological space, let \(A \subset X\), and let \(B \subset X\). Let \(\overline{A}\) denote the closure of~\(A\). Prove that
\[
\overline{A \cup B}=\overline{A}\cup\overline{B}.
\]
\def\ProblemHeadingText{Problem 3.}
\item
Let~\(I\) be an arbitrary index set, and let
\[
X=\prod_{i\in I}X_i.
\]
 Prove that if each \(X_i\) is connected, then~\(X\) is connected. You may use the fact that a finite product of connected spaces is connected, without proving this fact.
\def\ProblemHeadingText{Problem 4.}
\item
Let \((X,d)\) be a metric space. Prove that if~\(X\) is sequentially compact, then~\(X\) is compact.

\par
Recall the definition: \(X\) is sequentially compact if and only if every sequence of points in~\(X\) has a subsequence which converges to a point of~\(X\).
\def\ProblemHeadingText{Problem 5.}
\item
Let \((X,d)\) be a nonempty complete metric space with no isolated points. Prove that~\(X\) is uncountable.

\par
Recall the definition: A point~\(x\) is an isolated point of~\(X\) if and only if the set \(\{x\}\) is open.
\def\ProblemHeadingText{Problem 6.}
\item
Prove that a compact Hausdorff (\(T_2\)) space is normal.
\def\ProblemHeadingText{Problem 7.}
\item
Define an equivalence relation~\(\sim\) on \(X=[0,1]\) by \(x\sim x\) for all~\(x\), \(0\sim 1\), and \(1\sim 0\). Prove that the quotient space \(X/{\sim}\) is homeomorphic to the circle \(S^1\).
\end{examproblems}
\subsection{Part 2.}
\begin{examinstructions}
Answer the following with complete definitions or statements or short proofs.
\end{examinstructions}
\begin{examproblems}{7}{H3}
\def\ProblemHeadingText{Problem 8.}
\item
Complete the following definition: Let \((X,\mathcal{T})\) be topological space, and let~\(A\) be a subset of~\(X\). The relative topology or subspace topology on~\(A\) is defined as follows:
\def\ProblemHeadingText{Problem 9.}
\item
Complete the following definition: Let~\(E\) be a set, and let~\(\mathcal{B}\) be a collection of subsets of~\(E\). We say that~\(\mathcal{B}\) is a basis for a topology on~\(E\) if and only if
\def\ProblemHeadingText{Problem 10.}
\item
Complete the following definition: Let~\(I\) be any set, and let \(\{(X_i,\mathcal{T}_i):i\in I\}\) be an indexed family of topological spaces. Let
\[
X=\prod_{i\in I}X_i.
\]
 The product topology on~\(X\) is defined as follows.
\def\ProblemHeadingText{Problem 11.}
\item
State the Extreme Value Theorem.
\def\ProblemHeadingText{Problem 12.}
\item
State the Contraction Mapping Theorem. (This theorem is also known as the Banach Fixed Point Theorem.)
\def\ProblemHeadingText{Problem 13.}
\item
Let~\(X\) denote the set of real numbers with the finite complement topology. Let~\(Y\) denote the set of real numbers with the usual topology. Does there exist a continuous, surjective (onto) function \(f:X\to Y\)?
\end{examproblems}
\end{document}
