\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Analysis PhD Exam, January 2026},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Analysis PhD Exam, January 2026}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/analysis-phd/}{Analysis PhD Exam}, January 2026\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Analysis PhD Exam, January 2026}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examinstructions}
Write solutions in a neat and logical fashion, giving complete reasons for all steps. Do six of eight.
\end{examinstructions}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
Do two of three.
\begin{examsubparts}
\item[\textnormal{(i)}]
Give an example of a Lebesgue measurable set \(E\subseteq[0,1]\) that is closed, has positive measure, but contains no non-trivial interval or explain why no such example exists.
\item[\textnormal{(ii)}]
Is the function \(g:\mathbb R\to\mathbb R\) defined by \(g(x)=\frac{1}{1+x^2}\) the Hardy–Littlewood maximal function of an \(L^1(\mathbb R)\) function~\(f\)?
\item[\textnormal{(iii)}]
Does there exist a measure space \((X,\mathcal M,\mu)\) and a nested decreasing sequence \((E_n)_{n=1}^{\infty}\) of measurable sets such that
\[
\lim_{n\to\infty}\mu(E_n)\ne\mu\left(\bigcap_{n=1}^{\infty}E_n\right)?
\]
\end{examsubparts}
\def\ProblemHeadingText{Problem 2.}
\item
Suppose \(f:[0,1]\times[0,1]\to\mathbb R\). Show that if the following conditions hold, then \(F:[0,1]\to\mathbb R\) defined by
\[
F(x)=\int_{[0,1]}f(x,y)\,d\lambda(y)
\]
 is continuous. Here~\(\lambda\) denotes Lebesgue measure on \(\mathbb R\).
\begin{examsubparts}
\item[\textnormal{(a)}]
For each \(x\in[0,1]\) the function \(g_x(y)=f(x,y)\) is continuous;
\item[\textnormal{(b)}]
For each \(y\in[0,1]\) the function \(h_y(x)=f(x,y)\) is continuous; and
\item[\textnormal{(c)}]
\(f\) is bounded.
\end{examsubparts}
\def\ProblemHeadingText{Problem 3.}
\item
Let \((X,\mathcal M)\) denote a measurable space and let \(P(X)\) denote the power set of~\(X\). Prove, if \(\mathcal M\ne P(X)\) and \(\{x\}\in\mathcal M\) for each \(x\in X\), then there exists an \(A\notin\mathcal M\otimes\mathcal M\) such that \([A]_x,[A]^y\in\mathcal M\) for all \(x,y\in X\). Suggestion: First show \(\delta:X\to X\times X\) defined by \(\delta(x)=(x,x)\) is measurable from \((X,\mathcal M)\) to \((X\times X,\mathcal M\otimes\mathcal M)\).
\def\ProblemHeadingText{Problem 4.}
\item
Suppose \((X,\mathcal M,\mu)\) is a measure space and \(f,g:X\to[0,\infty)\) are measurable. Show:
\begin{examsubparts}
\item[\textnormal{(a)}]
\(\mu_f:\mathcal M\to[0,\infty]\) defined by \(\mu_f(A)=\int\chi_Af\,d\mu=\int_Af\,d\mu\) is a measure; and
\item[\textnormal{(b)}]
\(\int g\,d\mu_f=\int gf\,d\mu\).
\end{examsubparts}
\def\ProblemHeadingText{Problem 5.}
\item
Do two of three. Short answer: you do not need to give a detailed proof, just a brief explanation.
\begin{examsubparts}
\item[\textnormal{(a)}]
If \(a_1,\ldots,a_n\) are nonnegative real numbers, must it be the case that
\[
\left(\sum_{j=1}^n a_j\right)^6\le n^5\sum_{j=1}^n a_j^6?
\]
\item[\textnormal{(b)}]
Explain why, given \(x\in[0,1]\), the mapping \(E_x:C([0,1])\to\mathbb C\) defined by \(E_x(f)=f(x)\) is a bounded linear functional. Is the dual of the Banach space \(C([0,1])\) separable?
\item[\textnormal{(c)}]
Give an example where the Radon–Nikodym Theorem fails without the sigma-finite hypothesis.
\end{examsubparts}
\def\ProblemHeadingText{Problem 6.}
\item
Let \(\mathbb C[x]\) denote the complex vector space of polynomials in~\(x\). Does there exist a norm \(\|\cdot\|\) on \(\mathbb C[x]\) such that \((\mathbb C[x],\|\cdot\|)\) is a Banach space. Provide a proof for your answer.
\def\ProblemHeadingText{Problem 7.}
\item
Suppose \(\phi,\psi\) are bounded linear functionals on a Hilbert space~\(V\). Show, if \(\|\phi+\psi\|=\|\phi\|+\|\psi\|\), then one of \(\phi,\psi\) is a multiple of the other. Is the result still true if~\(V\) is only assumed to be a Banach space?
\def\ProblemHeadingText{Problem 8.}
\item
Show if \(f\in L^1(\mathbb R)\) and \(g\in L^\infty(\mathbb R)\), then the convolution \(f*g\) is continuous. Let \(E\subseteq[0,1]\) be a Lebesgue measurable set of positive measure and let
\[
-E=\{-x:x\in E\}.
\]
 By considering the function \(h=\chi_{-E}*\chi_E\) or otherwise, show
\[
E-E=\{x-y:x,y\in E\}
\]
 contains an open interval.
\end{examproblems}
\end{document}
