\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Algebra PhD Exam, May 2001},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Algebra PhD Exam, May 2001}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/algebra-phd/}{Algebra PhD Exam}, May 2001\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Algebra PhD Exam, May 2001}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examinstructions}
Do seven of the following eleven problems. Please do not turn in more than seven problems. You must show your work. Answers with no work and/or no explanations will receive no credit. State clearly any theorem you use in your proofs. In the problems, \(\mathbb Z\), resp. \(\mathbb Q, \mathbb C\), is the set of all integers, resp. of all rational numbers, of all complex numbers.
\end{examinstructions}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
Let~\(G\) be a finite group of order \(m\cdot n\) and~\(K\) a normal subgroup of~\(G\) of order~\(m\), where~\(m\) and~\(n\) are coprime.
\begin{examsubparts}
\item[\textnormal{(i)}]
Prove that~\(G\) has exactly one subgroup of order~\(m\).
\item[\textnormal{(ii)}]
Suppose that~\(n\) is a prime power. Is there any subgroup~\(H\) of~\(G\) such that~\(G\) is a semidirect product of~\(K\) by~\(H\)? Justify your answer.
\end{examsubparts}
\def\ProblemHeadingText{Problem 2.}
\item
Prove that any finite group of order \(616=11\cdot 8\cdot 7\) is solvable. You may assume that every group of order \(p^a q^b\), where~\(p\) and~\(q\) are primes, is solvable.
\def\ProblemHeadingText{Problem 3.}
\item
Let \(\mathrm{GL}_2(\mathbb C)\) be the group of invertible \(2\times 2\) complex matrices under matrix multiplication and let~\(G\) be a finite subgroup of \(\mathrm{GL}_2(\mathbb C)\). Suppose that~\(G\) is simple and \(|G|\) is even. Prove that \(|G|=2\). (Hint: Consider elements of order 2 of~\(G\).)
\def\ProblemHeadingText{Problem 4.}
\item
Let~\(A\) be a \(3\times 3\) complex matrix. Suppose that \(\operatorname{Tr}(A)=\operatorname{Tr}(A^2)=\operatorname{Tr}(A^3)=0\) (where \(\operatorname{Tr}(X)\) is the trace of the square matrix~\(X\)). Prove that \(A^{2001}=0\).
\def\ProblemHeadingText{Problem 5.}
\item
Let~\(q\) be a prime power and~\(F\) a field of~\(q\) elements. Find the number \(N(q)\) of monic irreducible polynomials of degree 2 over~\(F\).
\def\ProblemHeadingText{Problem 6.}
\item
Let~\(p\) be a prime. Let~\(K\) be a subfield of \(\mathbb C\) with the property: “If~\(E\) is a finite extension of~\(K\) such that \([E:K]\) is coprime to~\(p\), then \(E=K\).” Prove that if~\(F\) is any finite extension of~\(K\), then \([F:K]\) is a~\(p\)-power. (Hint: Use normal closure, Galois Theory, and Sylow’s Theorem.)
\def\ProblemHeadingText{Problem 7.}
\item
Let \(\xi\in\mathbb C\) be such that \(\xi^{2001}=5\). Show that \(\mathbb Q(\xi)\) cannot be contained in any cyclotomic extension of \(\mathbb Q\).
\def\ProblemHeadingText{Problem 8.}
\item
Compute the integral closure~\(R\) of \(\mathbb Z\) in \(\mathbb Q(\sqrt{-5})\). Is~\(R\) a unique factorization domain? A principal ideal domain? A Dedekind domain? Justify your answer(s).
\def\ProblemHeadingText{Problem 9.}
\item
Let~\(R\) be a local ring. Prove that every finitely generated projective~\(R\)-module is free.
\def\ProblemHeadingText{Problem 10.}
\item
State and prove the Hilbert Nullstellensatz.
\def\ProblemHeadingText{Problem 11.}
\item
Let~\(R\) be a primitive ring such that \(ab-ba\) is nilpotent for all \(a,b\in R\). Prove that~\(R\) is a division ring.
\end{examproblems}
\end{document}
