\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Topology PhD Exam, August 1994},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Topology PhD Exam, August 1994}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/topology-phd/}{Topology PhD Exam}, August 1994\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Topology PhD Exam, August 1994}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\subsection{PART I}
\begin{examinstructions}
State each of the following theorems and prove one of them.
\end{examinstructions}
\begin{examproblems}{0}{H3}
\def\ProblemHeadingText{Problem 1.}
\item
Tychonoff Product Theorem
\def\ProblemHeadingText{Problem 2.}
\item
Baire Category Theorem
\def\ProblemHeadingText{Problem 3.}
\item
Brouwer Fixed Point Theorem
\def\ProblemHeadingText{Problem 4.}
\item
Tietze Extension Theorem
\def\ProblemHeadingText{Problem 5.}
\item
Schoenflies Theorem for \(\mathbb{R}^2\). Does the corresponding statement hold for \(\mathbb{R}^3\)? Explain.
\end{examproblems}
\subsection{PART II}
\begin{examinstructions}
For the following problems give proofs as well as conclusions. Your proofs should be clear and detailed, you should show all your work, and your writing must be legible.
\end{examinstructions}
\begin{examproblems}{0}{H3}
\def\ProblemHeadingText{Problem 1.}
\item
Compute the fundamental group of the projective plane, \(P^2\).
\def\ProblemHeadingText{Problem 2.}
\item
Compute the homology groups and the Euler characteristic of the Klein bottle.
\def\ProblemHeadingText{Problem 3.}
\item
Let \(D^n=\{x\in\mathbb{R}^n:|x|\leq 1\}\) be the~\(n\)-dimensional disk. Show that every continuous map \(f:S^3\to D^n\) is homotopic to a constant map.
\def\ProblemHeadingText{Problem 4.}
\item
This problem has two parts.
\begin{examsubparts}
\item[\textnormal{(a)}]
Prove that the Cantor set~\(C\) is totally disconnected.
\item[\textnormal{(b)}]
If \(f:C\to[0,1]\) is a continuous map from the Cantor set to the closed unit interval, must~\(f\) omit a value in \([0,1]\)? (I.e., must there exist a \(y\in[0,1]\) such that \(f(x)=y\) has no solution \(x\in C\)?)
\end{examsubparts}
\def\ProblemHeadingText{Problem 5.}
\item
For \(i=1,2,3,\ldots\), let \(X_i\) be a great circle in the~\(2\)-sphere \(S^2=\{x\in\mathbb{R}^3:|x|=1\}\). Show that \(S^2\neq\bigcup_{i=1}^{\infty}X_i\).
\end{examproblems}
\end{document}
