\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Combinatorics PhD Exam, May 2024},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Combinatorics PhD Exam, May 2024}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/combinatorics-phd/}{Combinatorics PhD Exam}, May 2024\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Combinatorics PhD Exam, May 2024}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
This problem has two parts.
\begin{examsubparts}
\item[\textnormal{(a)}]
Let \(g(n)\) be the number of all permutations of length~\(n\) in which every cycle length is odd. Find the closed form of the exponential generating function of the sequence \(g(n)\).
\item[\textnormal{(b)}]
Let \(h(n)\) be the number of all permutations of length~\(n\) in which every cycle length is odd and the total number of cycles is odd. Find the closed form of the exponential generating function of the sequence \(h(n)\).
\end{examsubparts}
\def\ProblemHeadingText{Problem 2.}
\item
Prove that a balanced, uniform design is regular. (A design is balanced if every pair of vertices belong to the same number of blocks. A design is uniform if each block contains the same number of vertices. A design is regular if every vertex lies in the same number of blocks.)
\def\ProblemHeadingText{Problem 3.}
\item
Prove among any choice of 26 points inside the unit square, there are two points within distance \(0.29\) of each other.
\def\ProblemHeadingText{Problem 4.}
\item
Let~\(G\) be a simple graph with more than 200 edges. Is it true that if~\(G\) does not have a vertex of degree at least 11, then~\(G\) must contain a matching consisting of at least 11 edges? Explain.
\def\ProblemHeadingText{Problem 5.}
\item
Prove that the poset \(\mathbb{N}^k\) does not contain an infinite antichain. (For \(u,v\in\mathbb{N}^k\) we define \(u\leq v\) if \(u_i\leq v_i\) for all \(i\in[k]\).)
\def\ProblemHeadingText{Problem 6.}
\item
Let \(f:[n]\to[n]\) be a function. Let us call~\(f\) an acyclic function if the diagram of~\(f\), that is, the directed graph on vertex set \([n]\) that has an edge from~\(i\) to~\(j\) when \(f(i)=j\), has no cycles longer than one. Find a formula for the number of all acyclic functions on \([n]\).
\def\ProblemHeadingText{Problem 7.}
\item
Find the number of permutations of length nine whose descent set is \(\{3,7\}\).
\def\ProblemHeadingText{Problem 8.}
\item
This problem has two parts.
\begin{examsubparts}
\item[\textnormal{(a)}]
Let~\(C\) be a composition of~\(n\), and let \(X(C)\) be the number of parts of~\(C\). Find \(\mathbb{E}(X)\).
\item[\textnormal{(b)}]
Let~\(C\) be a composition of~\(n\), and let \(Y(C)\) be the number of parts of~\(C\) that are equal to 1. Find \(\mathbb{E}(Y)\).
\end{examsubparts}
\end{examproblems}
\end{document}
