\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Analysis First-Year Exam, August 2017, Part 1},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\renewcommand{\labelenumi}{\textbf{\theenumi.}}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\newenvironment{examproblems}[1]{%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\section{\@startsection{section}{1}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=Title}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/analysis-first-year/}{Analysis First-Year Exam}, August 2017, Part 1\par}%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Analysis First-Year Exam, August 2017, Part 1}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examinstructions}
Answer FOUR questions in detail. State carefully any results used without proof.
\end{examinstructions}
\begin{examproblems}{0}
\item
\(A\) and~\(B\) are nonempty sets of real numbers such that: (i) \(A \cup B = \mathbb{R}\) and (ii) \(a < b\) whenever \(a \in A\) and \(b \in B\). Prove that there exists a unique \(s \in \mathbb{R}\) such that \((−\infty,s) \subseteq A\) and \((s,\infty) \subseteq B\).
\item
Let~\(X\) be a metric space, of which~\(A\) and~\(B\) are compact subsets; define \(\delta := \inf\{d(a,b):a \in A,b \in B\}\). Prove that there exist \(a_0 \in A\) and \(b_0 \in B\) such that \(d(a_0,b_0)=\delta\). Must \(a_0\) and \(b_0\) be unique? Proof or counterexample, as appropriate.
\item
Let~\(f\) be a surjective map from the precompact metric space~\(X\) onto the metric space~\(Y\). Prove that if~\(f\) is uniformly continuous then~\(Y\) is also precompact. Show by example that if uniformly is dropped then~\(Y\) can fail to be precompact.
\item
Let \(f:\mathbb{R}\to\mathbb{R}\) be continuous. Can it be the case that for each \(t \in \mathbb{R}\), the value \(f(t)\) is irrational iff~\(t\) itself is rational? If yes, give an example; if no, give a proof.
\item
Let \(f:(0,\infty)\to\mathbb{R}\) be differentiable and assume that \(f(t)\to\ell \in \mathbb{R}\) as \(t\to\infty\). Prove that if \(f'(t)\to L \in \mathbb{R}\) as \(t\to\infty\) then \(L=0\).
\end{examproblems}
\end{document}
