\DocumentMetadata{
  pdfversion=2.0,
  pdfstandard=ua-2,
  lang=en-US,
  tagging=on,
  tagging-setup={math/setup=mathml-SE,tabsorder=structure}
}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.68in,includefoot]{geometry}
\usepackage{newcomputermodern}
\usepackage{amsmath,amscd,mathtools}
\usepackage{tikz,adjustbox}
\providecommand{\square}{\mdlgwhtsquare}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Variational Analysis/Numerical Optimization PhD Exam, January 2026},
  pdfauthor={University of Florida Department of Mathematics},
  pdfsubject={Graduate mathematics examination},
  pdfdisplaydoctitle=true,
  bookmarksopen=true
}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}
\setlength{\emergencystretch}{3em}
\setlength{\leftmargini}{2.15em}
\setlength{\leftmarginii}{2.65em}
\setlength{\leftmarginiii}{3em}
\pagestyle{empty}
\raggedbottom
\allowdisplaybreaks
\NewTaggingSocketPlug{block/list/label}{examproblem}{%
  \tagstructbegin{tag=Lbl}\tagstructend%
  \tagstructbegin{tag=\LBody}%
  \tagstructbegin{tag=\ProblemHeadingTag,title-o={\ProblemHeadingText}}%
  \tagmcbegin{tag=\ProblemHeadingTag,actualtext={\ProblemHeadingText}}%
  #2%
  \tagmcend%
  \tagstructend%
}
\newenvironment{examproblems}[2]{%
  \def\ProblemHeadingTag{#2}%
  \AssignTaggingSocketPlug{block/list/label}{examproblem}%
  \begin{enumerate}%
  \setcounter{enumi}{#1}%
  \renewcommand{\labelenumi}{\textbf{\theenumi.}}%
  \setlength{\topsep}{0.35em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.48em}%
  \setlength{\parsep}{0.18em}%
}{\end{enumerate}}
\newenvironment{examsubparts}{%
  \AssignTaggingSocketPlug{block/list/label}{default}%
  \begin{enumerate}%
  \setlength{\topsep}{0.18em}%
  \setlength{\partopsep}{0pt}%
  \setlength{\itemsep}{0.16em}%
  \setlength{\parsep}{0.1em}%
}{\end{enumerate}}
\newenvironment{examinstructions}{%
  \par\begingroup\itshape
}{%
  \par\endgroup\vspace{0.18em}
}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{0pt}%
  {-1.25ex plus -.25ex minus -.1ex}%
  {0.55ex plus .1ex}%
  {\normalfont\large\bfseries}}
\renewcommand{\@maketitle}{%
  \newpage\null\vskip -1em%
  {\footnotesize\bfseries
    \href{https://www.ufl.edu/}{University of Florida}, \href{https://math.ufl.edu/}{Department of Mathematics}\par}%
  \vskip -0.5em%
  \tagstructbegin{tag=H1,title={Variational Analysis/Numerical Optimization PhD Exam, January 2026}}%
  \tagpdfparaOff%
  \tagmcbegin{tag=H1}%
    {\LARGE\bfseries\href{https://gma.math.ufl.edu/exams/numerical-optimization-phd/}{Variational Analysis/Numerical Optimization PhD Exam}, January 2026\par}%
  \tagmcend%
  \tagpdfparaOn%
  \tagstructend%
  \vskip 0.25em%
  \tagmcbegin{artifact}%
    \hrule height 1pt%
  \tagmcend%
  \vskip 1em%
}
\makeatother
\title{Variational Analysis/Numerical Optimization PhD Exam, January 2026}
\author{}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{examinstructions}
Do 8 problems, 4 from problems 1–5 and 4 from problems 6–10.
\end{examinstructions}
\begin{examproblems}{0}{H2}
\def\ProblemHeadingText{Problem 1.}
\item
Recall that \(f:\mathbb{R}^n\to\mathbb{R}\) is convex if and only if
\[
f[(1-\alpha)\mathbf{x}+\alpha\mathbf{y}]\leq (1-\alpha)f(\mathbf{x})+\alpha f(\mathbf{y})
\]
 for all \(\mathbf{x},\mathbf{y}\in\mathbb{R}^n\) and \(\alpha\in[0,1]\).
\begin{examsubparts}
\item[\textnormal{(a)}]
If~\(f\) is continuously differentiable, then show that~\(f\) is convex if and only if
\[
f(\mathbf{y})\geq f(\mathbf{x})+\nabla f(\mathbf{x})(\mathbf{y}-\mathbf{x})
\]
 for all \(\mathbf{x},\mathbf{y}\in\mathbb{R}^n\).
\item[\textnormal{(b)}]
If~\(f\) is twice continuously differentiable, then show that~\(f\) is convex if and only if \(\nabla^2f\) is positive semidefinite on \(\mathbb{R}^n\).
\end{examsubparts}
\def\ProblemHeadingText{Problem 2.}
\item
Given \(\mathbf{x}_0\in\mathbb{R}^n\), let \(0<\sigma<\mu<1\) be Wolfe line search parameters. In a Wolfe line search for minimizing \(f:\mathbb{R}^n\to\mathbb{R}\), \(\mathbf{x}_{k+1}=\mathbf{x}_k-s_k\mathbf{g}_k\), where \(\mathbf{g}_k=\nabla f(\mathbf{x}_k)^T\), and the stepsize \(s_k\) at step~\(k\) is chosen so that the following two conditions hold:

\par
W1. \(F(s_k)\leq F_L(s_k)\), where \(F(s)=f(\mathbf{x}_k-s\mathbf{g}_k)\) and \(F_L(s)=f(\mathbf{x}_k)-\sigma s\lVert\mathbf{g}_k\rVert^2\).

\par
W2. \(F'(s_k)\geq\mu F'(0)=-\mu\lVert\mathbf{g}_k\rVert^2\).

\par
If~\(f\) is bounded from below, prove that there exists a stepsize \(s_k>0\) satisfying the Wolfe conditions. If~\(f\) is twice continuously differentiable over the convex hull of the level set
\[
L=\{\mathbf{x}\in\mathbb{R}^n:f(\mathbf{x})\leq f(\mathbf{x}_0)\},
\]
 and the largest eigenvalue of \(\nabla^2f\) is bounded by \(M<\infty\) over~\(L\), then prove that the gradient \(\mathbf{g}_k\) converges to zero.
\def\ProblemHeadingText{Problem 3.}
\item
Suppose \(f:\mathcal{K}\to\mathbb{R}\), where \(\mathcal{K}\subset\mathbb{R}^n\) is a convex set.
\begin{examsubparts}
\item[\textnormal{(a)}]
If \(\mathbf{x}^*\) is a local minimizer of~\(f\), then show that
\[
\nabla f(\mathbf{x}^*)(\mathbf{x}-\mathbf{x}^*)\geq 0\qquad\text{for all }\mathbf{x}\in\mathcal{K}. \tag{1}
\]
\item[\textnormal{(b)}]
If~\(f\) is convex over~\(\mathcal{K}\) and differentiable at some point \(\mathbf{x}^*\in\mathcal{K}\) where (1) holds, then show that \(\mathbf{x}^*\) is a global minimizer for~\(f\) over~\(\mathcal{K}\).
\item[\textnormal{(c)}]
Consider the quadratic programming problem
\[
\min \frac{1}{2}\mathbf{x}^T\mathbf{A}\mathbf{x}-\mathbf{b}^T\mathbf{x}\qquad\text{subject to }\mathbf{x}\in\mathcal{K},
\]
 where \(\mathcal{K}\subset\mathbb{R}^n\) is a closed convex set and \(\mathbf{A}\in\mathbb{R}^{n\times n}\) is positive definite with smallest eigenvalue \(\alpha>0\). Show that the solutions \(\mathbf{u}_i\), \(i=1,2\), associated with \(\mathbf{b}=\mathbf{b}_i\), \(i=1,2\), respectively, satisfy
\[
\lVert\mathbf{u}_1-\mathbf{u}_2\rVert\leq \lVert\mathbf{b}_1-\mathbf{b}_2\rVert/\alpha.
\]
\end{examsubparts}
\def\ProblemHeadingText{Problem 4.}
\item
Prove the arithmetic-geometric mean inequality:
\[
\left(\prod_{i=1}^n x_i\right)^{1/n}\leq \frac{1}{n}\sum_{i=1}^n x_i
\]
 where \(\mathbf{x}\geq 0\). Hint: change variables to \(\mathbf{y}=c\mathbf{x}\), where~\(c\) is a scalar chosen so that the components of~\(\mathbf{y}\) sum to 1. Note that maximizing the product of the \(y_i\) is equivalent to maximizing the log of the product since \(\log(t)\) is a monotone increasing function of~\(t\) on \((0,\infty)\). Using duality, the max of the log of the product can be determined explicitly.
\def\ProblemHeadingText{Problem 5.}
\item
Consider the quadratic program
\[
\min \frac{1}{2}\mathbf{x}^T\mathbf{A}\mathbf{x}-\mathbf{b}^T\mathbf{x}\qquad\text{subject to }\mathbf{a}^T\mathbf{x}=c, \tag{2}
\]
 where~\(\mathbf{A}\) is a symmetric, positive definite matrix. The penalty approximation to (2) is
\[
\min \frac{1}{2}\mathbf{x}^T\mathbf{A}\mathbf{x}-\mathbf{b}^T\mathbf{x}+\frac{p}{2}(\mathbf{a}^T\mathbf{x}-c)^2, \tag{3}
\]
 where \(p>0\) is the penalty parameter. Use the first-order optimality conditions for both (2) and (3) to obtain a bound for the distance between the solution of (2) and the solution of (3).
\def\ProblemHeadingText{Problem 6.}
\item
Let us consider the minimization problem
\[
\min I(y):=\int_0^1 f(y'(x),y(x),x)\,dx\qquad\text{subject to }y\in C_0^1, \tag{4}
\]
 where~\(f\) is a given continuously differentiable function. If \(y^*\) is a local minimizer of this problem, \(s\) is a scalar, \(h\in C_0^1\), then setting to zero the derivative of \(I(y^*+sh)\) evaluated at \(s=0\) yields the following first-order optimality condition:
\[
\int_0^1\left[\left(\frac{\partial f}{\partial y'}\right)^*(x)h'(x)+\left(\frac{\partial f}{\partial y}\right)^*(x)h(x)\right]dx=0 \tag{5}
\]
 for all \(h\in C_0^1\), where
\[
\left(\frac{\partial f}{\partial y'}\right)^*(x):=\frac{\partial f}{\partial y'}(y^{*'}(x),y^*(x),x)
\quad\text{and}\quad
\left(\frac{\partial f}{\partial y}\right)^*(x):=\frac{\partial f}{\partial y}(y^{*'}(x),y^*(x),x).
\]
\begin{examsubparts}
\item[\textnormal{(a)}]
As a consequence of (5), show that
\[
\left(\frac{\partial f}{\partial y'}\right)^*\in C^1 \tag{6}
\]
 and the Euler equation is satisfied. Note that it is only assumed that~\(f\) is continuously differentiable; you should show that at a local minimizer of (4), the partial derivative in (6) is continuously differentiable.
\item[\textnormal{(b)}]
For the special case
\[
f(y'(x),y(x),x)=\frac{1}{2}y'(x)^2-\varphi(x)y(x)^2,
\]
 where \(\varphi\in C^k\) for some integer \(k\geq 0\), what does the observation in (a) imply concerning the smoothness of a minimizer \(y^*\) for (4)?
\end{examsubparts}
\def\ProblemHeadingText{Problem 7.}
\item
Suppose that~\(P\) and~\(Q\) are real-valued functions defined on the interval \([0,1]\), with~\(P\) continuously differentiable and~\(Q\) continuous. It is assumed that there exists \(\alpha>0\) such that \(P(x)\geq\alpha\) for all \(x\in[0,1]\). Define
\[
\text{[missing functional symbol]}(h):=\int_0^1 P(x)h'(x)^2+Q(x)h(x)^2\,dx.
\]
 Suppose that \(\text{[missing functional symbol]}\) has the following property: There exists \(\text{[missing positive constant]}>0\) such that
\[
\text{[missing functional symbol]}(h)\geq \text{[missing positive constant]}\int_0^1 h'(x)^2+h(x)^2\,dx\qquad\text{for all }h\in H_0^1,
\]
 where \(H_0^1\) is the space of functions with \(h'\) square integrable over \([0,1]\) and \(h(0)=h(1)=0\).

\par
Prove the following: If~\(u\) is a solution of the boundary-value problem
\[
\frac{d}{dx}(P(x)u'(x))=Q(x)u(x)\qquad\text{for all }x\in[0,a],\qquad u(0)=0=u(a),
\]
 where \(a\in(0,1)\) is given, then~\(u\) vanishes on the entire interval \([0,a]\). Hint: extend~\(u\) from \([0,a]\) to \([0,1]\) by setting \(u(x)=0\) for \(x\in[a,1]\). Then integrate by parts to show that \(\text{[missing functional symbol]}(u)=0\).
\def\ProblemHeadingText{Problem 8.}
\item
Consider the variational problem
\[
\min \int_0^1\left(\frac{1}{2}u'(x)^2+e^{u(x)}\right)dx\qquad\text{subject to }u\in H_0^1. \tag{7}
\]
\begin{examsubparts}
\item[\textnormal{(a)}]
What is the first-order necessary optimality condition (Euler equation) for a local minimizer of this variational problem?
\item[\textnormal{(b)}]
Show that if a minimizer of (7) exists, then it is unique.
\end{examsubparts}
\def\ProblemHeadingText{Problem 9.}
\item
Consider the initial-value problem
\[
\dot{\mathbf{x}}(t)=\mathbf{A}(t)\mathbf{x}(t)+\mathbf{u}(t),\qquad \mathbf{x}(0)=0,
\]
 where \(\mathbf{x}:[0,1]\to\mathbb{R}^n\) and \(\mathbf{A}\in L^\infty([0,1];\mathbb{R}^{n\times n})\). Obtain a bound for the sup-norm of~\(\mathbf{x}\) in terms of the \(L^2\) norm of~\(\mathbf{u}\). Hint: Recall Grönwall’s inequality
\[
x(t)\leq\alpha(t)+L\int_0^t x(s)\,ds\text{ on }[0,a]\quad\Rightarrow\quad x(t)\leq\alpha(t)e^{Lt}\text{ on }[0,a],
\]
 where~\(\alpha\) is monotone nondecreasing.
\def\ProblemHeadingText{Problem 10.}
\item
Consider the following control problem:
\[
\min \int_0^1\left(\frac{1}{2}u^2(x)+y(x)\right)dx\qquad\text{subject to }y'(x)=u(x),\quad y(0)=0,\quad u(x)\geq\ell(x),
\]
 where \(\ell(x)\) is a given lower bound for the control \(u(x)\) at each \(x\in[0,1]\).
\begin{examsubparts}
\item[\textnormal{(a)}]
What is the first-order optimality condition (Pontryagin minimum principle) for this problem?
\item[\textnormal{(b)}]
What is the solution of the control problem?
\end{examsubparts}
\end{examproblems}
\end{document}
